Forecasting U.S. Food Market Prices: A Bayesian Hierarchical Approach

### 2024-12-14 paper/paper.qmd
final fixes

# install.packages("broom.mixed")
# install.packages("tidybayes")
# install.packages("bayesplot")
library(knitr)
library(ggplot2)
library(dplyr)
library(arrow)
library(rstanarm)
library(modelsummary)
library(brms)
library(broom.mixed)
library(kableExtra)
library(tidybayes)
library(bayesplot)

>>>>

# Install packages if not available already
# install.packages("broom.mixed")
# install.packages("tidybayes")
# install.packages("bayesplot")

library(knitr)
library(ggplot2)
library(dplyr)
library(arrow)
library(rstanarm)
library(modelsummary)
library(brms)
library(broom.mixed)
library(kableExtra)
library(tidybayes)
library(bayesplot)
